Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Combine papers on measuring data quality

Several authors have investigated the \emph{meaning} of data quality, how to 
\emph{measure} it and what \emph{impact} poor data quality has on software 
projects.

@@

The first study came to several conclusions, among which:
  \begin{itemize}
    \item closed source software projects usually exhibit better data quality 
    (i.e. better average number of attachments, better average status changes, 
    better average number of commits per bug report);
    \item reduced traceability between bug reports and version control logs
    due to scarce linkage between the two;
    \item open source projects exhibit reduced quality in change logs as,
    for example, the Eclipse project has over 20\% empty commit messages.
  \end{itemize}
However, the second study reached the conclusion that representational data 
quality dimensions are underlying causes of accessibility data quality problem
patterns. The authors also found out that three underlying causes for users'
complaints regarding data not supporting their tasks are incomplete data, 
inadequately defined or measured data and data that could not be appropriately
aggregated.

Several authors have investigated the application quality metrics to ticket 
data.

\textbf{Data Quality in Context}\cite{strong1997data}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the authors was to analyze data quality in different 
    organizations, observe data quality problem patterns as well as see 
    its implications.
  \item \textbf{What was the method?}
    They performed a qualitative analysis, examining 42 data quality projects 
    from 3 organizations. They collected data via interviews of data procedures,
    custodians, customers and managers. The authors analysed each project using
    the data quality dimensions as content analysis codes. 
  \item \textbf{What did they learn?}
    One thing that the authors learned is that representational data quality 
    dimensions are underlying causes of accessibility data quality problem 
    patterns. Also, they observed three underlying causes for users' complaints
    regarding data not supporting their tasks:
      \begin{itemize}
        \item incomplete data;
        \item inadequately defined or measured data;
        \item data that could not be appropriately aggregated.
      \end{itemize}
  \item \textbf{Relevance to our work}: this paper brings valuable insight into
    major data quality issues and patterns, information which we can apply in 
    our own research.
\end{itemize}

\textbf{Data Quality Assessment}\cite{pipino2002data}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the authors is to present ways of developing usable data
    quality metrics that organizations can implement in their own internal 
    processes.
  \item \textbf{What was the method?}
    They have researched previous methods of assessing data quality in information
    systems and they formulated general advice that can be directly implemented
    by organizations in their processes.
  \item \textbf{What did they learn?}
    They learned that there is no universal approach to assessing data quality
    as it heavily depends on the context where it is analysed.
  \item \textbf{Relevance to our work}: it shows how one can effectively measure
    data quality in information systems, thus we can apply it on the quality of
    the tickets we are analysing.
\end{itemize}

\textbf{Product perspective on total Data Quality Assessment}\cite{wang1998product}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The author wanted to create a Total Data Quality Management methodology so that
    high quality information products could be delivered to information consumers.
  \item \textbf{What was the method?}
    The research presents us, firstly, with a couple of definitions for the methodology:
      \begin{itemize}
        \item TDQM cycle - define, measure, analyze and improve information quality continuously;
        \item information product - information output from an information manufacturing system
          that has value to the information consumer;
        \item information quality - fitness for use by information consumers.
      \end{itemize}
    Then, the author presents the four steps in order to successfully implement the TDQM methodology:
      \begin{itemize}
        \item clearly articulate the information product;
        \item establish several roles that would be in charge of the information product management;
        \item teach information quality assessment and management skills to all IP constituencies;
        \item institutionalize continuous information product improvement.
      \end{itemize}
  \item \textbf{What did they learn?}
    The author learned that this methodology is filling a gap in the information quality
    world and that it could help organizations better manage the information quality of their
    information products.
  \item \textbf{Relevance to our work}
    This article could prove helpful to our own research as the methodology presented could help
    us in detecting if there is data quality in the projects we will be analyzing.
\end{itemize}

@@

 \textbf{AIMQ}\cite{lee2002aimq}:
 \begin{itemize}
   \item \textbf{What were the goals?}
     The main challenge set by the authors was to develop an overall model
     with an accompanying assessment instrument for quantifying information
     quality.
   \item \textbf{What was the method?}
     They developed a methodology called AIM quality (hence the name AIMQ) which
     they applied at 5 different organizations. It has 3 main components:
      \begin{itemize}
        \item 2 $\times$ 2 model of what information quality means to managers;
        \item questionnaire for measuring information quality along the dimensions
          found in first step;
        \item two analysis techniques for interpreting the assessments captured 
          by the questionnaire.
      \end{itemize} 
   \item \textbf{What did they learn?}
      They conclude that the AIMQ methodology proved to be a practical information
      quality tool to organizations.
   \item \textbf{Relevance to our work}: the paper gave us valuable insight into 
     how to assess information quality.
\end{itemize}

>>>>

Several authors have investigated the \emph{meaning} of data quality and
what characteristics define it.

@@

The first study came to several conclusions, among which:
  \begin{itemize}
    \item closed source software projects usually exhibit better data quality 
    (i.e. better average number of attachments, better average status changes, 
    better average number of commits per bug report);
    \item reduced traceability between bug reports and version control logs
    due to scarce linkage between the two;
    \item open source projects exhibit reduced quality in change logs as,
    for example, the Eclipse project has over 20\% empty commit messages.
  \end{itemize}

However, the second study reached the conclusion that representational data 
quality dimensions are underlying causes of accessibility data quality problem
patterns. The authors also found out that three underlying causes for users'
complaints regarding data not supporting their tasks are incomplete data, 
inadequately defined or measured data and data that could not be appropriately
aggregated.

After defining what data quality is and what are its characteristics, the next 
step would be how to measure data or information quality in a project.

There are several research papers that try to find the answer, among which the 
work of \citet{lee2002aimq}. The authors tried to define an overall model along 
with an accompanying assessment instrument for quantifying information quality 
in an organization. The methodology has 3 main steps that need to be followed 
in order to apply it successfully:
  \begin{itemize}
    \item 2 $\times$ 2 model of what information quality means to managers;
    \item questionnaire for measuring information quality along the dimensions
    found in first step;
    \item two analysis techniques for interpreting the assessments captured 
    by the questionnaire.
  \end{itemize} 
After developing the technique, they applied it at 5 different organizations and
found that the tool proved to be practical.

Compared to the methodology proposed by \citet{lee2002aimq}, the solution found
by \citet{Heinrich2007MetricsDataQuality} is quite different. Even though the 
main goals were the same, the authors used a single metric, and that is 
the metric for timeliness (i.e. whether the values of attributes still 
correspond to the current state of their real world counterparts and whether 
they are out of date). Thus, they applied the metric at a major German mobile 
services provider. Due to some Data Quality issues the company was having, they 
had lower mailing campaign success rates, but after applying the metrics, the 
company was able to establish a direct connection between the results of
measuring data quality and the success rates of campaigns.

Another important area of data quality is what methodologies can be applied by
organizations in order to improve it. There are several studies that tried to
propose such methodologies. A general overview of such techniques was presented 
by \citet{pipino2002data} - they wanted to present ways of developing usable 
data quality methods that organizations can implement in their own internal 
processes. After reviewing various techniques of assessing data quality in
information systems, they reached the conclusion that there is no universal 
approach to assess data quality as it heavily depends on the context where it is
analysed.

One such methodology examined by \citet{pipino2002data} is the technique 
proposed by \citet{wang1998product} called Total Data Quality Management
(abbreviated TDQM). Through this method, the authors wanted to help 
organizations deliver high quality information products to information
consumers by following the TDQM cycle - define, measure, analyse and improve
information quality continuously. In order to do that, the research proposes
4 steps: clearly articulate the information product, establish several roles
that would be in charge of the information product management, teach information
quality assessment and management skills to all information products 
constituencies and, finally, institutionalize continuous information product 
improvement. After developing the methodology, the authors conclude on a 
confident note that their technique can fill a gap in the information quality
environment.

@@
